Through the eyes of the teacher

### 2021-03-01 paper_1/paper_1_supplement_new_table.Rmd
update GRI (calib - lesson + head - intervention)

teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
  filter(perspective == "self-assessment")%>%
  group_by(scale) %>%
  summarise("M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value),
            "Cronbach's α" = mean(alpha))

@@

# create a basic table (tibble) using tidyverse functions for teacher self assessment 
student.scale.quest.table <- quest.raw.data.alpha %>% # select data
  filter(perspective == "student")%>%
  group_by(scale) %>%
  summarise("M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value),
            "Cronbach's α" = mean(alpha))

@@

>>>>

teacher.scale.quest.table <- quest.raw.data.alpha %>% # select data
  filter(perspective == "self-assessment")%>%
  group_by(scale) %>%
  summarise("N items" = n_distinct(shortID),
            "M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value),
            "Cronbach's α" = mean(alpha))

@@

# create a basic table (tibble) using tidyverse functions for teacher self assessment 
student.scale.quest.table <- quest.raw.data.alpha %>% # select data
  filter(perspective == "student")%>%
  group_by(scale) %>%
  summarise("N items" = n_distinct(shortID),
            "M" = round(mean(value), 2),
            "SD" = round(sd(value), 2),
            "Min" = min(value),
            "Max" = max(value),
            "Skewness" = skewness(value),
            "Kurtosis" = kurtosis(value),
            "Cronbach's α" = mean(alpha))

@@

```{r Calib end to lession start TOI, echo = FALSE}

# prepare data (selected from questionnaire data)
et.calib.lesson.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_calib_end_lesson_start.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.calib.lesson.data <- et.calib.lesson.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
                                       )
options(digits = 2)

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.calib.lesson.table <- et.calib.lesson.data %>%
  group_by(Participant, Variable1) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Fixation Duration" = Total_duration_of_whole_fixations,
            "M Duration Fixation" = Average_duration_of_whole_fixations,
            "TOI" = Duration_of_interval,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)

# format and insert table in manuscript
apa_table(
  et.calib.lesson.table,
  caption = "Number and Duration (in msec) of Fixations Calibration End to Lesson Start",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

```{r Disturbance "head on table" to first intervention, echo = FALSE}

# prepare data (selected from questionnaire data)
et.distub.head.data<-read.table("./data/Aperol_pilot_glasses_raw_metrics_head_on_table_session1.tsv", dec=",", sep="\t", header=T)

# converting integer to numeric
et.distub.head.data <- et.distub.head.data %>%  mutate(Duration_of_interval = as.numeric(Duration_of_interval),
                                       Total_duration_of_whole_fixations = as.numeric(Total_duration_of_whole_fixations),
                                       Number_of_whole_fixations = as.numeric(Number_of_whole_fixations),
                                       Average_duration_of_whole_fixations = as.numeric(Average_duration_of_whole_fixations)
                                       )
options(digits = 2)

# calculate the GRI 
# create a basic table (tibble) using tidyverse functions
et.distub.head.table <- et.distub.head.data %>%
  group_by(Participant, Variable1) %>%
  summarise("Fixation Number" = Number_of_whole_fixations,
            "Fixation Duration" = Total_duration_of_whole_fixations,
            "M Duration Fixation" = Average_duration_of_whole_fixations,
            "TOI" = Duration_of_interval,
            "GRI" = Average_duration_of_whole_fixations / Number_of_whole_fixations)
view(et.distub.head.data)

# format and insert table in manuscript
apa_table(
  et.distub.head.table,
  caption = "Number and Duration (in msec) of Fixations for Disturbance 'head on table' to first intervention",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "scriptsize" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

### 2021-03-01 paper_1/paper_1_supplement_new_table.tex
update GRI (calib - lesson + head - intervention)

\begin{tabular}{llllllll}
\toprule
scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
\midrule
Activation and support & 2.46 & 1.14 & 1 & 4 & 0.10 & 1.65 & 0.85\\
Clarity and structuredness & 2.81 & 0.91 & 1 & 4 & -0.17 & 2.17 & -0.76\\
Classroom management & 2.44 & 0.88 & 1 & 4 & 0.19 & 2.38 & 0.83\\
Natural behaviour & 2.83 & 0.76 & 2 & 4 & 0.28 & 1.84 & 0.90\\
Positive climate and motivation & 2.85 & 0.87 & 1 & 4 & -0.49 & 2.65 & 0.78\\
Presence: posture/gaze & 2.70 & 1.01 & 1 & 4 & -0.44 & 2.15 & 0.85\\
Presence: verbal and non-verbal intervention & 2.75 & 0.79 & 1 & 4 & -0.07 & 2.48 & -0.75\\
Presence: voice & 2.79 & 0.72 & 2 & 4 & 0.32 & 2.03 & 0.77\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{llllllll}
\toprule
scale & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
\midrule
Activation and support & 2.64 & 1.13 & 1 & 4 & -0.32 & 1.73 & 0.48\\
Clarity and structuredness & 3.58 & 0.68 & 1 & 4 & -1.75 & 6.09 & 0.62\\
Classroom management & 3.18 & 0.91 & 1 & 4 & -0.87 & 2.86 & 0.75\\
Natural behaviour & 3.43 & 0.67 & 2 & 4 & -0.74 & 2.46 & 0.85\\
Positive climate and motivation & 3.41 & 0.83 & 1 & 4 & -1.40 & 4.29 & 0.82\\
Presence: posture/gaze & 3.24 & 0.89 & 1 & 4 & -1.05 & 3.31 & 0.59\\
Presence: verbal and non-verbal intervention & 3.18 & 0.81 & 1 & 4 & -0.66 & 2.70 & 0.20\\
Presence: voice & 3.60 & 0.60 & 2 & 4 & -1.18 & 3.36 & 0.71\\
\bottomrule
\end{tabular}

@@

@@

We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{moments} {[}Version 0.14; Komsta and Novomestky (2015){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{sjPlot} {[}Version 2.8.7; Lüdecke (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al. (2019){]} for all our analyses.

@@

@@

@@

@@

>>>>

\begin{tabular}{lllllllll}
\toprule
scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
\midrule
Activation and support & 3 & 2.46 & 1.14 & 1 & 4 & 0.10 & 1.65 & 0.85\\
Clarity and structuredness & 2 & 2.81 & 0.91 & 1 & 4 & -0.17 & 2.17 & -0.76\\
Classroom management & 4 & 2.44 & 0.88 & 1 & 4 & 0.19 & 2.38 & 0.83\\
Natural behaviour & 3 & 2.83 & 0.76 & 2 & 4 & 0.28 & 1.84 & 0.90\\
Positive climate and motivation & 6 & 2.85 & 0.87 & 1 & 4 & -0.49 & 2.65 & 0.78\\
Presence: posture/gaze & 7 & 2.70 & 1.01 & 1 & 4 & -0.44 & 2.15 & 0.85\\
Presence: verbal and non-verbal intervention & 3 & 2.75 & 0.79 & 1 & 4 & -0.07 & 2.48 & -0.75\\
Presence: voice & 3 & 2.79 & 0.72 & 2 & 4 & 0.32 & 2.03 & 0.77\\
\bottomrule
\end{tabular}

@@

\begin{tabular}{lllllllll}
\toprule
scale & \multicolumn{1}{c}{N items} & \multicolumn{1}{c}{M} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} & \multicolumn{1}{c}{Skewness} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Cronbach's a}\\
\midrule
Activation and support & 3 & 2.64 & 1.13 & 1 & 4 & -0.32 & 1.73 & 0.48\\
Clarity and structuredness & 2 & 3.58 & 0.68 & 1 & 4 & -1.75 & 6.09 & 0.62\\
Classroom management & 4 & 3.18 & 0.91 & 1 & 4 & -0.87 & 2.86 & 0.75\\
Natural behaviour & 3 & 3.43 & 0.67 & 2 & 4 & -0.74 & 2.46 & 0.85\\
Positive climate and motivation & 6 & 3.41 & 0.83 & 1 & 4 & -1.40 & 4.29 & 0.82\\
Presence: posture/gaze & 7 & 3.24 & 0.89 & 1 & 4 & -1.05 & 3.31 & 0.59\\
Presence: verbal and non-verbal intervention & 3 & 3.18 & 0.81 & 1 & 4 & -0.66 & 2.70 & 0.20\\
Presence: voice & 3 & 3.60 & 0.60 & 2 & 4 & -1.18 & 3.36 & 0.71\\
\bottomrule
\end{tabular}

@@

\caption{\label{tab:Calib end to lession start TOI}Number and Duration (in msec) of Fixations Calibration End to Lesson Start}

\begin{tabular}{lllllll}
\toprule
Participant & \multicolumn{1}{c}{Variable1} & \multicolumn{1}{c}{Fixation Number} & \multicolumn{1}{c}{Fixation Duration} & \multicolumn{1}{c}{M Duration Fixation} & \multicolumn{1}{c}{TOI} & \multicolumn{1}{c}{GRI}\\
\midrule
01\_01\_D & Expert & 101.00 & 38,177.00 & 378.00 & 53,133.00 & 3.74\\
01\_02\_A & Expert & 27.00 & 6,736.00 & 249.00 & 15,502.00 & 9.22\\
01\_03\_B & Novice & 57.00 & 36,378.00 & 638.00 & 58,763.00 & 11.19\\
01\_04\_C & Novice & 65.00 & 22,387.00 & 344.00 & 39,235.00 & 5.29\\
02\_01\_A & Novice & 14.00 & 2,619.00 & 187.00 & 30,195.00 & 13.36\\
02\_02\_B & Novice & 46.00 & 15,851.00 & 345.00 & 30,297.00 & 7.50\\
02\_03\_C & Novice & 86.00 & 27,643.00 & 321.00 & 42,603.00 & 3.73\\
02\_04\_D & Novice & 53.00 & 27,783.00 & 524.00 & 36,204.00 & 9.89\\
\bottomrule
\end{tabular}

@@

We used R {[}Version 4.0.3; R Core Team (2019){]} and the R-packages \emph{\}dplyr} {[}@\}R-dplyr{]}, \emph{corrplot2017} (Wei \& Simko, 2017), \emph{forcats} {[}Version 0.5.0; Wickham (2020a){]}, \emph{Formula} {[}Version 1.2.4; Zeileis and Croissant (2010){]}, \emph{ggplot2} {[}Version 3.3.2; Wickham (2016){]}, \emph{Hmisc} {[}Version 4.4.2; Harrell Jr, Charles Dupont, and others. (2020){]}, \emph{lattice} {[}Version 0.20.41; Sarkar (2008){]}, \emph{moments} {[}Version 0.14; Komsta and Novomestky (2015){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{papayar} (Muschelli, 2016), \emph{psych} {[}Version 2.0.12; Revelle (2020){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{readr} {[}Version 1.4.0; Wickham, Hester, and Francois (2018){]}, \emph{sjPlot} {[}Version 2.8.7; Lüdecke (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{survival} {[}Version 3.2.7; Terry M. Therneau and Patricia M. Grambsch (2000){]}, \emph{tibble} {[}Version 3.0.4; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.2; Wickham (2020b){]}, and \emph{tidyverse} {[}Version 1.3.0; Wickham et al. (2019){]} for all our analyses.

@@

\leavevmode\hypertarget{ref-R-Hmisc}{}%
Harrell Jr, F. E., Charles Dupont, with contributions from, \& others., many. (2020). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}

@@

\leavevmode\hypertarget{ref-R-lattice}{}%
Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}

@@

\leavevmode\hypertarget{ref-R-survival-book}{}%
Terry M. Therneau, \& Patricia M. Grambsch. (2000). \emph{Modeling survival data: Extending the {C}ox model}. New York: Springer.

\leavevmode\hypertarget{ref-R-corrplot2017}{}%
Wei, T., \& Simko, V. (2017). \emph{R package "corrplot": Visualization of a correlation matrix}. Retrieved from \url{https://github.com/taiyun/corrplot}

@@

\leavevmode\hypertarget{ref-R-Formula}{}%
Zeileis, A., \& Croissant, Y. (2010). Extended model formulas in {R}: Multiple parts and multiple responses. \emph{Journal of Statistical Software}, \emph{34}(1), 1--13. \url{https://doi.org/10.18637/jss.v034.i01}
